### 2016-09-07 sec4_baseline.tex
Revision inlcluded

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining (TRPM). (a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.  (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

@@

\begin{algorithm}[h]
\small
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

Based on the above theorem, under TRPM, every consecutive $\eta$ snapshots
form a partition. In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. Our next task is to design an efficient pattern mining strategy within each partition. Our solution includes a line sweep algorithm to sequentially scan the $\eta$ replicated snapshots in a partition and an effective candidate pattern enumeration mechanism.

Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process. It is initialized using the clusters with size no smaller than $M$ in the first snapshot. Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}).

After sweeping all the snapshots, all the valid patterns are stored in $C$ (Line~\ref{code:ls-valid-check}). 
It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered. Therefore, those patterns that do not appear in the $S_t$ are false candidates. In particular, our
three pruning rules are as follows:
First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joining with all clusters in $S_j$, 
candidates in $C$ with the maximum timestamp no smaller than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}). Third, candidates in $C$ with the size of the first segment smaller than $L$
are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ can be significantly reduced.

>>>>

\begin{figure*} [t]
\center
\includegraphics[width=0.85\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining (TRPM). (a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.  (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

@@

\vspace{-5mm}
\begin{algorithm}[h]
\small
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

Based on the above theorem, under TRPM, every consecutive $\eta$ snapshots
form a partition. In other words, each snapshot $S_t$ corresponds to a partition $\lambda_t=\{S_t,...,S_{t+\eta-1}\}$. 
Next, we aim to
%Our next task is to 
design an efficient pattern mining strategy within each partition. Our solution includes a line sweep algorithm to sequentially scan the $\eta$ %replicated 
snapshots in a partition and an effective candidate pattern enumeration mechanism.

Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping. It is initialized using the clusters with size no smaller than $M$ in the first snapshot. Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
Specifically, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}).

After sweeping all the snapshots, all the valid patterns are stored in $C$ (Line~\ref{code:ls-valid-check}). 
It is worth noting that $C$ continues to grow during the whole sweeping. We can use three pruning rules to early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered. Therefore, those patterns that do not appear in the $S_t$ are false candidates. In particular, our
three pruning rules are as follows:
First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joining with all clusters in $S_j$, 
candidates in $C$ with the maximum timestamp no smaller than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}). Third, candidates in $C$ with the size of the first segment smaller than $L$
are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ can be significantly reduced.

### 2016-09-07 sec5_spm.tex
Revision inlcluded

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{spm.eps}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned TRPM scheme replicates snapshots based on the temporal dimension which suffers from two drawbacks. First, the replication factor $\eta$ can be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
To resolve these limitations,
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second stage of the map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMPs. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

Before we introduce the Apriori Enumerator, we are interested to 
examine the issue of global vertex ordering on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among reducers. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

\begin{figure}[h]
\centering
\includegraphics[width=0.40\textwidth]{star-alt.eps}
\caption{Examples of star partitioning with different vertex orderings.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object ID to determine the vertex ordering in our implementation.

\subsection{Apriori Enumerator}
Intuitively, given a GCMP with an object set $\{o_1,o_2,\ldots,o_m\}$, 
all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
be connected in the associated temporal graphs $\{G_t\}$. This inspires us to leverage the classic Apriori algorithm~\cite{agrawal1994fast} to enumerate all the valid GCMPs starting from pairs of objects. However, we observe that the monotonicity property does not hold between an object set and its supersets.

@@

\begin{lemma}\label{lemma:subset-property}
If $T_1$ is a subset of $T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that $T_1'$ is a subset of $T_2'$.
\end{lemma}
\begin{proof}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

@@

It is possible that the simplified sequence $\mathtt{sim}(T)=\emptyset$. For example, Let $T=(1,2,5,6)$ 
and $L=3$. All the segments will be removed in the $f$-step and the output is $\emptyset$.
We define $\emptyset$ to be not decomposable. 
%Based on the above definitions, we can define our monotonicity to facilitate the pruning in the Apriori algorithm.
We then link \emph{sequence simplification} and \emph{decomposable sequence} in the following lemma:
%We provide an important property of the sequence simplification process as follows:
\begin{lemma}\label{lemma:decom-sim}
If sequence $T$ is a superset of any decomposable sequence, then $\mathtt{sim}(T) \neq \emptyset$.
\end{lemma}
\begin{proof}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.85\textwidth]{spm.eps}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned TRPM scheme replicates snapshots based on the temporal dimension which suffers from two drawbacks. First, the replication factor $\eta$ can be large. Second, the same valid pattern may be redundantly discovered from different partitions.
%which results in redundant works.
To resolve these limitations,
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second stage of the map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMPs. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

Before we introduce the Apriori Enumerator, we are interested to 
examine the issue of global vertex ordering.
% on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among reducers. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\caption{Star partitioning with different vertex orderings.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is dense, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object ID to determine the vertex ordering in our implementation.

\subsection{Apriori Enumerator}
Intuitively, given a GCMP with an object set $\{o_1,\ldots,o_m\}$, 
all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
be connected in the associated temporal graphs $\{G_t\}$. This inspires us to leverage the classic Apriori algorithm~\cite{agrawal1994fast} to enumerate all the valid GCMPs starting from pairs of objects. However, we observe that the monotonicity property does not hold between an object set and its supersets.

@@

\begin{lemma}\label{lemma:subset-property}
%If $T_1$ is a subset of $T_2$, 
If $T_1 \subseteq T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that %$T_1'$ is a subset of $T_2'$.
$T_1' \subseteq T_2'$.
\end{lemma}
\begin{proof}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

@@

It is possible that the simplified sequence $\mathtt{sim}(T)=\emptyset$. For example, Let $T=(1,2,5,6)$ 
and $L=3$. All the segments will be removed in the $f$-step and the output is $\emptyset$.
We define $\emptyset$ to be not decomposable. 
%Based on the above definitions, we can define our monotonicity to facilitate the pruning in the Apriori algorithm.
We then link \emph{sequence simplification} and \emph{decomposable sequence} in the following lemma:
%We provide an important property of the sequence simplification process as follows:
\begin{lemma}\label{lemma:decom-sim}
If sequence $T$ is a superset of any decomposable sequence, then $\mathtt{sim}(T) \neq \emptyset$.
\end{lemma}

\begin{proof}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.
